Report

### 2023-04-11 script/report.Rmd
update rmd

---
title: "to change"
author: " "
date: "2022-08-16"
output:
    html_document:
        highlight: tango
        number_sections: no
        theme: default
        toc: yes
        toc_depth: 3
        toc_float:
            collapsed: no
            smooth_scroll: yes
params:
  DP.min: DP.min
  AR.min: AR.min
  result_dir: result_dir
  rmd: "report.Rmd"
  AR: AR
---

```{r setup, include=FALSE}
# title: "`r params$title`"
knitr::opts_chunk$set(root.dir=workspace, echo = FALSE , warning=FALSE, error=TRUE, message=FALSE)
```

```{r }
library(tidyverse)
library(DT)
library(ggplot2)
library(plyr)
library(dplyr)
library(yaml)

@@

```{r}
workspace<-params$result_dir
```

## Trimming parameters

```{r trimmomatic}
trimmo<-paste0(workspace,"/01_sequence_qc/log/trimmomatic.log")
dat<-read.table(text=gsub(" ","\t",readLines(trimmo)),  header=TRUE)
DT::datatable(dat)
```

## Mapping parameters

### Flagstat results

```{r flagstat}
library(tidyverse)
file <- paste0(workspace,"/02_mapping/flagstat/concatenate_flagstat.txt")
if(file.exists(file)){
    flagstat <- read.table(file, sep="\t", header=FALSE) %>% 
      dplyr::mutate(mapped=V3-V4, unmapped=V2-V3, supplementary=V4, 
                    mapped.ratio=round(mapped/(mapped+unmapped)*100,2), 
                    unmapped.ratio=round(unmapped/(mapped+unmapped)*100,2),
                    supplementary.ratio=round(supplementary/(mapped+unmapped)*100,2)) %>% dplyr::select(-V2, -V3, -V4)
    names(flagstat) <- c("sample", "mapped", "unmapped", "supplementary", "mapped.ratio", "unmapped.ratio", "supplementary.ratio")

  }

DT::datatable(flagstat, options = list(rownames = TRUE, pageLength = 10, scrollX = T, dom = 'tip'),class = 'cell-border stripe')
#count
nbr.reads.melt <- flagstat %>% dplyr::select(sample, mapped, unmapped, supplementary) %>% reshape2::melt(id = "sample", value.name = "nbr.reads")
summary.nbr <- nbr.reads.melt %>% group_by(variable) %>% summarise(median=median(nbr.reads), max=max(nbr.reads), min=min(nbr.reads))
nbr.reads.melt <- left_join(nbr.reads.melt, summary.nbr, by = "variable") %>% mutate(x.label=paste0(variable, "\nmedian=", median, "\nmax=", max, "\nmin=", min))
ggplot(data = nbr.reads.melt, aes(y=nbr.reads, x=x.label)) + geom_boxplot()  + xlab("") + ylab("number of reads") + ggtitle("Boxplot representing the number of mapped/supplementary/unmapped reads")+theme_bw()
#ratio
ratio.reads.melt <- flagstat %>% dplyr::select(sample, mapped.ratio, supplementary.ratio) 
names(ratio.reads.melt) <- c("sample", "mapped", "supplementary")
ratio.reads.melt <- ratio.reads.melt %>% reshape2::melt(id = "sample", value.name = "ratio")
summary.ratio <- ratio.reads.melt %>% group_by(variable) %>% summarise( median=round(median(ratio),2), max=round(max(ratio),2), min=round(min(ratio),2))
ratio.reads.melt <- left_join(ratio.reads.melt, summary.ratio, by = "variable") %>% mutate(x.label=paste0(variable, "\nmedian=", median, "%\nmax=", max, "%\nmin=", min, "%"))
ggplot(data = ratio.reads.melt) + geom_boxplot(aes(y=ratio, x=x.label)) + xlab("") + ylab("% reads") + scale_y_continuous(breaks = seq(0, max(ratio.reads.melt$ratio)+10, 20)) + ggtitle("Boxplot representing the percentage of mapped reads and supplementary alignments")+theme_bw()

@@

```{r SNV_InDels_calling.Rmd}

@@

```{r SV_calling.Rmd}

@@

```{r tDNA_scan.Rmd}

@@

# Tools used

```{r tools}

>>>>

---
title: "Report"
author: " "
date: "2022-08-16"
output:
    html_document:
        highlight: tango
        number_sections: no
        theme: default
        toc: yes
        toc_depth: 3
        toc_float:
            collapsed: no
            smooth_scroll: yes
params:
  DP.min: DP.min
  AR.min: AR.min
  result_dir: result_dir
  rmd: "report.Rmd"
  AR: AR
---

```{r setup, include=FALSE}
# title: "`r params$title`"
workspace <- "/Users/nbentahar/Documents/PROJECTs/DEV/msgenova/examples/soj/results/"
#workspace<-params$result_dir

sample_sheet.file <- "/Users/nbentahar/Documents/PROJECTs/DEV/msgenova/examples/soj/sample_sheet_soj_3samples.txt"

knitr::opts_chunk$set(root.dir=workspace, echo = FALSE , warning=FALSE, error=TRUE, message=FALSE)
```

```{r }
library(DT)
library(ggplot2)
library(vcfR)
library(dplyr)
library(yaml)

@@

```{r}

sample_sheet <- read.table(file = sample_sheet.file, header = TRUE, sep = "\t")

@@

```{r quality_control.Rmd}

  out <- c(out, knitr::knit_child("quality_control.Rmd"), quiet=TRUE)

```{r SNV_InDels_calling.Rmd, eval=FALSE}

vcf.file <- "/Users/nbentahar/Documents/PROJECTs/DEV/msgenova/examples/soj/results/03_snv_indels_calling/SOJ_snv_indel.vcf"

@@

```{r SV_calling.Rmd, eval=FALSE}

@@

```{r tDNA_scan.Rmd, eval=FALSE}

@@

```{r tools, eval=FALSE}
